\documentclass[11pt]{article}


\usepackage{multirow}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{bbm}
\usepackage{graphics}
\usepackage{float}
\usepackage{times}
\usepackage{hhline}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}

% disable default indenting
\setlength{\parindent}{0pt}

\usepackage{setspace}
\singlespacing

\usepackage{enumitem}
\setlist{nolistsep}

\newcommand{\head}[1]{ %
   % \bigskip %
    \bigskip %
    \begin{large}\begin{bf}{#1}\end{bf}\end{large} %

    \ \\ [-1.3cm] %

    \hrulefill}
\newcommand{\subhead}[1]{\textbf{#1}}

\begin{document}

%\pagenumbering{gobble}

\centerline{ \LARGE Philip Andrew White }
\smallskip
\centerline{ (801) 422-4870 $\bullet$ 2177 WVB $\bullet$ Provo, UT 84602 }
\smallskip
\centerline{pwhite@stat.byu.edu }
\smallskip

%\hrulefill

\head{Education}

\begin{enumerate}[label=$\bullet$]
\item Doctor of Philosophy: Statistical Science; Duke University; 2019
\begin{enumerate}[label=$\cdot$]
\item Dissertation: Topics in Bayesian Spatiotemporal Prediction of Environmental Exposure
\item Committee: Alan Gelfand (chair), Fan Li (co-chair), Colin Rundel, and Ben Goldstein
\end{enumerate}

\item Master of Science: Statistics; Brigham Young University; 2015

\begin{enumerate}[label=$\cdot$]
\item Thesis: Bayesian Gaussian Process Model for Antarctic Surface Mass Balance and Proposing New Field Measurements
\item  Committee: C. Shane Reese (chair), William F. Christensen, and Shannon Tass
%\item GPA: 4.00/4.00
\end{enumerate}

\item Bachelor of Science: Applied Physics; Brigham Young University; 2014 

\begin{enumerate}[label=$\cdot$]
\item Graduated \emph{Magna Cum Laude}; speaker at college graduation
\item Senior Thesis: Bayesian Model for Antarctic Surface Mass Balance
\item Minors: Mathematics, Scandinavian Studies
% GPA: 3.98/4.00
\end{enumerate}
\end{enumerate}


\head{Professional Experience}

\begin{enumerate}[label=$\bullet$]

\item Assistant Professor; Brigham Young University; 2019 -- Present

\item Data Science Intern: Disease Risk Modeling; The Climate Corporation; 2018

\end{enumerate}


\vspace{2mm}
\head{Peer-Reviewed Publications}

\begin{enumerate}[label=$\bullet$]


\item L. Warr$^\dagger$, M. Heaton, W. Christensen, \textbf{P. White}, and S. Rupper (2022+), ``Distributional Validation of Precipitation Data Products with Spatially Varying Mixture Models,'' accepted at \emph{Journal of Agricultural, Biological and Environmental Statistics}.

\item M. Heiner, M. Heaton, B. Abbott, \textbf{P. White}, C. Minaudo, and R. Dupas (2022+), ``Model-based clustering of trends and cycles of nitrate concentrations in Rivers across France,'' accepted at \emph{Journal of Agricultural, Biological and Environmental Statistics}.




\item D. Sheanshang$^\dagger$, \textbf{P. White}, and D. Keeler (2021+), ``Outlier Accommodation with Semiparametric Density Processes: A Study of Antarctic Snow Density Modelling,'' in press at \emph{Statistical Modelling}. \href{https://doi.org/10.1177/1471082X211043946}{link}

\item \textbf{P. White}, H. Frye, M. Christensen, A. Gelfand, and J. Silander Jr (2022), ``Spatial Functional Data Modeling of Plant Reflectances,'' \emph{Annals of Applied Statistics}, Volume 16, No. 3, 1919-1936. \href{http://dx.doi.org/10.1214/21-AOAS1576}{link}

\item X. Emery, E. Porcu, and \textbf{P. White} (2022), ``New Validity Conditions for the Multivariate Mat\'ern Coregionalization Model, with an Application to Exploration Geochemistry,'' \emph{Mathematical Geosciences}, Volume 54, 1043–1068. \href{https://link.springer.com/article/10.1007/s11004-022-10000-6}{link} 



\item \textbf{P. White}, D. Keeler, D. Sheanshang$^\dagger$, and S. Rupper (2022), ``Improving Piecewise Linear Snow Density Models through Hierarchical Spatial and Orthogonal Functional Smoothing,'' \emph{Environmetrics}, Volume 33, No. 5, e2726. \href{http://doi.org/10.1002/env.2726}{link}


\item  E. Porcu and \textbf{P. White} (2022), ``Random Fields on the Hypertorus: Covariance Modeling and Applications,'' \emph{Environmetrics}, Volume 33, No. 1, e2701. \href{https://doi.org/10.1002/env.2701}{link}

 \item A. Bowie, W. Zhou,  J. Tan, \textbf{P. White}, T. Stoinski, S. Yangjie, and B. Hare (2022), ``Motivating children's cooperation to conserve forests,'' \emph{Conservation Biology}, Volume 36, No. 4 , e13922. \href{https://conbio.onlinelibrary.wiley.com/doi/10.1111/cobi.13922}{link}


\item G. Cleanthous, E. Porcu, and \textbf{P. White} (2021), ``Regularity and Approximation of Gaussian Random Fields Evolving Temporally over Two-Point Homogeneous Spaces,'' \textit{TEST}, Vol. 30, No. 4, 836-860.  \href{https://link.springer.com/article/10.1007/s11749-021-00755-1}{link}


%\item $^*$A. Alegr\'ia, P.G. Bissiri, G. Cleanthous, E. Porcu, and \textbf{P. White} (2021+), ``Multivariate Isotropic Random  Fields on Spheres: Nonparametric Bayesian Modeling and $L^p$-Fast Approximations,''  accepted at Electronic Journal of Statistics
%\item D. Sheanshang$^\dagger$, \textbf{P. White}, and D. Keeler (2021+), ``Outlier Accommodation with Semiparametric Density Processes: A Study of Antarctic Snow Density Modelling,'' accepted at Statistical Modelling

\item H. Salomons, K. Smith, M. Callahan-Beckel, M. Callahan, K. Levy, B. Kennedy, E. Bray, G. Gnanadesikan, D. Horschler, M. Gruen, J. Tan, \textbf{P. White}, E. MacLean, and B. Hare (2021), ``Cooperative Communication with Humans Evolved to Emerge Early in Domestic Dogs,'' \textit{Current Biology}, Vol. 31, No. 14, 3137-3144. \href{https://www.cell.com/current-biology/fulltext/S0960-9822(21)00880-0}{link} 


\item \textbf{P. White}, D. Keeler, and S. Rupper (2021), ``Hierarchical Integrated Spatial Process Modeling of Monotone West Antarctic Snow Density Curves,'' \textit{Annals of Applied Statistics}, Vol. 15, No. 2, 556-571. \href{http://dx.doi.org/10.1214/21-AOAS1443}{link}

\item $^*$A. Alegr\'ia, P.G. Bissiri, G. Cleanthous, E. Porcu, and \textbf{P. White} (2021), ``Multivariate Isotropic Random  Fields on Spheres: Nonparametric Bayesian Modeling and $L^p$-Fast Approximations,'' \emph{Electronic Journal of Statistics}, Vol. 15, No. 1,  2360-2392. \href{https://doi.org/10.1214/19-EJS1593}{link}.
\item \textbf{P. White} and A. Gelfand (2021), ``Generalized Evolutionary Point Processes: Model Specifications and Model Comparison,''\emph{Methodology and Computing in Applied Probability}, Vol. 23, 1001–1021 (2021). \href{https://doi.org/10.1007/s11009-020-09797-8}{link}.
\item \textbf{P. White} and A. Gelfand (2021), ``Multivariate Functional Data Modeling with Time-varying Clustering,'' \textit{TEST}, Vol. 30, No. 3, 586–602. \href{http://link.springer.com/article/10.1007/s11749-020-00733-z}{link}
\item M. Gruen, \textbf{P. White}, and B. Hare (2020), ``Do Dog Breeds Differ in Pain Sensitivity? Veterinarians and the Public Believe They Do,'' \emph{PLoS ONE}, 15(3): e0230315. \href{https://doi.org/10.1371/journal.pone.0230315}{link}.
\item \textbf{P. White}, C.S. Reese, W. Christensen, and S. Rupper (2019), ``A Model for Antarctic Surface Mass Balance and Ice Core Site Selection,'' \emph{Environmetrics}, Volume 30, No. 8, e2579. \href{https://onlinelibrary.wiley.com/doi/abs/10.1002/env.2579}{link}.
\item \textbf{P. White} and E. Porcu (2019), ``Towards a Complete Picture of Stationary Covariance Functions on Spheres Cross Time,'' \emph{Electronic Journal of Statistics}, Vol. 13, No. 2, 2566-2594. \href{https://doi.org/10.1214/19-EJS1593}{link}.
\item \textbf{P. White}, A. Gelfand, E. Rodrigues, and G. Tzintzun (2019), ``Pollution State Modeling for Mexico City,'' \emph{Journal of the Royal Statistical Society - Series A}, Volume 182, No. 3, 1039-1060. \href{https://rss.onlinelibrary.wiley.com/doi/abs/10.1111/rssa.12444}{link}.
\item \textbf{P. White} and E. Porcu (2019), ``Nonseparable Covariance Models on Circles Cross Time: A Study of Mexico City Ozone,'' \emph{Environmetrics}, Volume 30, No. 5, e2558. \href{https://onlinelibrary.wiley.com/doi/full/10.1002/env.2558}{link}
\item \textbf{P. White}, C. Berrett, S. Tass, and M. Findlay (2019), ``Modeling Efficiency of Foreign Aid Allocation in Malawi,'' \emph{The American Statistician}, Volume 73, No. 4, 385-399.  \href{https://www.tandfonline.com/doi/full/10.1080/00031305.2018.1470032}{link}
\item \textbf{P. White}, A. Gelfand, and T. Utlaut (2017), ``Prediction and model comparison for areal unit data,'' \emph{Spatial Statistics}, Volume 22, Part 1, 89-106. \href{http://www.sciencedirect.com/science/article/pii/S2211675317301422}{link}
\item J. S. Colton, D. Meyer, K. Clark, D. Craft, J. Cutler, T. Park, and \textbf{P. White} (2012), ``Long-Lived electron spins in a modulation doped (100) GaAs quantum well,'' \emph{Journal of Applied Physics}, Volume 112, No. 8, 084307.  \href{http://aip.scitation.org/doi/abs/10.1063/1.4759320}{link}
\end{enumerate}

\emph{Submitted/Under Review/In Revisions}

\begin{enumerate}[label=$\bullet$]


\item E. Porcu, \textbf{P. White}, and M. Genton, ``"Nonseparable Space-Time Stationary Covariance Functions on Networks cross Time''. \href{https://arxiv.org/abs/2208.03359}{link}

\item G. Cleanthous, A. G. Georgiadis, and \textbf{P. White}, ``"Density estimation on metric spaces associated with operators and applications in seismology''.


\item $^*$A. Alegr\'ia, G. Cleanthous, A. Georgiadis, E. Porcu, and \textbf{P. White}, ``Random Fields on the Hypertorus: Regularities and Approximations''. 

\item C. Althoff, D. Cutchins, and \textbf{P. White}, ``A Cognitive Adaptation Study''. 
\setlength\itemsep{-1em} \\
\item[$*$] \textit{Under the request of one or more coauthors, the authors are listed in alphabetical order.}\\
\item[$\dagger$] \textit{Mentored Student co-author}
\end{enumerate}

\head{Other Publications}

\begin{enumerate}[label=$\bullet$]
\item P. White (2019), ``Topics in Bayesian Spatiotemporal Prediction of Environmental Exposure,'' Ph.D. Dissertation, Duke University.
\item P. White (2015), ``Bayesian Gaussian Process Model for Antarctic Accumulation and Proposing New Field Measurement,'' Masters Project, Brigham Young University.
\item P. White (2014), ``ORCA final report,'' \emph{2014 Journal of Undergraduate Research} [Online], Brigham Young University.
\item P. White (2014), ``Quantifying Climate Change: Bayesian Model for Antarctic Surface Mass Balance,'' Senior Thesis, Brigham Young University.
\end{enumerate}


\head{Posters and Presentations}

\begin{enumerate}[label=$\bullet$]

%\item The 15th International Conference of the ERCIM WG on Computational and Methodological Statistics, CMStatistics (2022), Invited Talk, ``Scalable Warped Directional Traffic Network Models for Traffic Accident Data''.

%\item ASA ENVR Workshop (2022), Contributed Poster, ``Spatial Functional Data Modeling of Plant Reflectances.''

\item Joint Statistical Meetings (2022), Topic-Contributed Talk, ``Spatial Functional Data Modeling of Plant Reflectances.''

\item Quality \& Productivity Research Conference (2022), Invited Talk, ``Some Challenges in Spatial Functional Data Analysis of West Antarctic Snow Density.''

\item National University of Ireland, Maynooth (2021), Invited Talk, ``Some Challenges in Spatial Functional Data Analysis of West Antarctic Snow Density.''

\item ICSA Applied Statistics Symposium (2021), Invited Talk, ``Hierarchical Integrated Spatial Process Modeling of Monotone West Antarctic Snow Density Curves.''

\item Joint Statistical Meetings (2021), Topic-Contributed Talk, ``Hierarchical Integrated Spatial Process Modeling of Monotone West Antarctic Snow Density Curves''.

\item The International Environmetrics Society (TIES) Virtual Conference (2020), Invited Talk, ``A Model for Antarctic Surface Mass Balance and Ice Core Site Selection''.
\item Brigham Young University Department of Statistics Seminar (2020), ``Hierarchical Integrated Spatial Process Modeling of Monotone West Antarctic Snow Density Curves''.
\item Joint Statistical Meetings (2020), Contributed Talk, ``Hierarchical Integrated Spatial Process Modeling of Monotone West Antarctic Snow Density Curves''.

\item New England Statistics Symposium (2019), Contributed Talk, ``Multivariate Functional Data Modeling with Time-varying Clustering''.
\item Joint Statistical Meetings (2019), Contributed Talk, ``Multivariate Functional Data Modeling with Time-varying Clustering''.

\item Brigham Young University Department of Statistics Seminar (2018), Invited Talk, ``Nonseparable Covariance Models on Circles Cross Time: A Study of Mexico City Ozone''.
\item The RAND Corporation (2018), Invited Talk, ``Nonseparable Covariance Models on Circles Cross Time: A Study of Mexico City Ozone''.
\item Los Alamos National Labs Seminar (2018), Invited Talk, ``Nonseparable Covariance Models on Circles Cross Time: A Study of Mexico City Ozone''.
\item Facebook Research Labs (2018), Invited Talk, ``Nonseparable Covariance Models on Circles Cross Time: A Study of Mexico City Ozone''.
%\item Duke Department of Statistical Science 701 Seminar Series (2018) -- Contributed Talk
\item International Conference on Advances in Interdisciplinary Statistics and Combinatorics (AISC) (2018), Contributed Talk, ``Nonseparable Covariance Models on Circles Cross Time: A Study of Mexico City Ozone''.
\item ASA ENVR Workshop - Statistics for the Environment: Research, Practice and Policy (2018), Contributed Poster, ``Pollution State Modeling for Mexico City''.

\item Society of Duke Fellows (2017), Invited Talk, ``Prediction and Model Comparison for Areal Unit Data''.
\item American Geophysical Union (2017), New Orleans, LA., Contributed Poster, ``A Model for Antarctic Surface Mass Balance and Ice Core Site Selection''. 
%\item Brigham Young University Student Research Conference (2015),  Provo, UT. -- Contributed Talk

\item Conference on Data Analysis (2014), Poster, Santa Fe, NM., Contributed Poster, ``A Model for Antarctic Surface Mass Balance and Ice Core Site Selection''. 


%\item ``Hierarchical Integrated Spatial Process Modeling of Monotone West Antarctic Snow Density Curves''
%\begin{enumerate}[label=$\cdot$]
%\item Brigham Young University Department of Statistics Seminar (2020) -- Invited Talk
%\item Joint Statistical Meetings (2020) -- Contributed Talk
%\end{enumerate}
%\item ``Multivariate Functional Data Modeling with Time-varying Clustering''
%\begin{enumerate}[label=$\cdot$]
%\item New England Statistics Symposium (2019) -- Contributed Talk
%\item Joint Statistical Meetings (2019) -- Contributed Talk
%\end{enumerate}
%\item ``Pollution State Modeling for Mexico City''
%\begin{enumerate}[label=$\cdot$]
%\item ASA ENVR Workshop - Statistics for the Environment: Research, Practice and Policy (2018) -- Contributed Poster
%\end{enumerate}
%\item ``Nonseparable Covariance Models on Circles Cross Time: A Study of Mexico City Ozone''.
%\begin{enumerate}[label=$\cdot$]
%\item Brigham Young University Department of Statistics Seminar (2018) -- Invited Talk
%\item RAND (2018) -- Invited Talk
%\item Los Alamos National Labs (2018) -- Invited Talk
%\item Facebook Research Labs (2018) -- Invited Talk
%%\item Duke Department of Statistical Science 701 Seminar Series (2018) -- Contributed Talk
%\item International Conference on Advances in Interdisciplinary Statistics and Combinatorics (AISC) (2018) -- Contributed Talk
%\end{enumerate}
%\item ``Prediction and Model Comparison for Areal Unit Data''
%\begin{enumerate}[label=$\cdot$]
%%\item Duke Department of Statistical Science 701 Seminar Series (2018) -- Contributed Talk
%\item Society of Duke Fellows (2017) -- Invited Talk
%\end{enumerate}
%\item  ``A Model for Antarctic Surface Mass Balance and Ice Core Site Selection,'' 
%\begin{enumerate}[label=$\cdot$]
%%\item 2020 TIES Conference (2020), Virtual. -- Invited Talk.
%\item American Geophysical Union (2017), New Orleans, LA. -- Contributed Poster
%%\item Brigham Young University Student Research Conference (2015),  Provo, UT. -- Contributed Talk
%\item Conference on Data Analysis (2014), Poster, Santa Fe, NM. --  Poster
%%\item Brigham Young University Student Research Conference (2014), Provo, UT. -- Contributed Talk
%\end{enumerate}
%\item  ``Photoluminescence Decays in Cadmium Telluride,'' 
%\begin{enumerate}[label=$\cdot$]
%\item Brigham Young University Student Research Conference (2013), Provo, UT. -- Contributed Talk
%\end{enumerate}
\end{enumerate}

\head{Courses Taught}

\begin{enumerate}[label=$\bullet$]
\item Instructor of Record
\begin{enumerate}[label=$\cdot$]
\item Brigham Young University
\begin{enumerate}[label=$\cdot$]
\item Statistics 330 (Introduction to Regression): Winter 2020, 2021
\item Statistics 641 (Probability Theory \& Mathematical Statistics 1): Fall 2019, 2020, 2021, 2022
\item Swedish 201: Winter 2012 
\item Swedish 202: Fall 2011, Fall 2012
\end{enumerate}
\item Duke University
\begin{enumerate}[label=$\cdot$]
\item Statistics 111 (Probability and Statistics): Summer I 2017
\end{enumerate}
\end{enumerate}
\item Teaching Assistant
\begin{enumerate}[label=$\cdot$]
\item Duke University
\begin{enumerate}[label=$\cdot$]
\item Statistics 322/522 (Design of Surveys and Causal Studies): Spring 2019
\item Statistics 944 (Spatial Statistics): Fall 2018
\item Statistics 444/644 (Spatio-temporal Modeling): Spring 2018, Fall 2018
\item Statistics 532 (Theory of Inference): Fall 2017
\item Statistics 111 (Probability and Statistics): Spring 2017 
\end{enumerate}
\end{enumerate}
\end{enumerate}

\head{Grant Submissions and Funding}


\begin{enumerate}[label=$\bullet$]
\item Funded
\begin{enumerate}[label=$\cdot$]
\item 2021-2023 ``Point Process Models for Traffic Risk Analysis and Crash Prevention, the National Science Foundation, 2020 (Role: Co-PI, Amount: \$199,941).
\item 2021-2022 (Funded). ``The Role of Temperature Variation for Reconstructing the Advance and Retreat of Glacial Ice using Thermal and Radar Imaging,'' Brigham Young University Interdisciplinary Research (IDR) Origination Awards, 2020 (Role: Co-PI, Amount: \$119,910).

\end{enumerate}
%\item Pending
%\begin{enumerate}[label=$\cdot$]
%%\item 2021-2023 (Submitted). ``Point Process Models for Traffic Risk Analysis and Crash Prevention, Submitted to the National Science Foundation, 2020 (Role: Co-Investigator, Amount: \$200,000).
%\end{enumerate}
\item Not Funded
\begin{enumerate}[label=$\cdot$]
\item 2021-2023. ``Atmospheric Drivers of West Antarctic Ice Sheet Surface Mass Balance,'' Submitted to the National Aeronautics and Space Administration, 2020 (Role: PI for BYU portion, Amount: \$249,289).
\item 2020-2022. ``Analysis Methods for Multivariate Point Patterns on Linear Networks,'' submitted to the National Science Foundation, 2019 (Role: Co-PI, Amount: \$310,946).
\item 2020-2022. `Quantifying Snow and Glacier Response to Climate and Aerosol Forcings in High Mountain Asia,'' submitted to the National Aeronautics and Space Administration, 2019 (Role: PI for BYU portion; Amount: \$256,328).
\end{enumerate}
\end{enumerate}

\head{Fellowships, Scholarships, and Awards}
\begin{enumerate}[label=$\bullet$]

\item The 2020 BYU Department of Statistics Young Scholar Faculty Fellowship (Amount: \$6,000)
\item 2019 Wiley-TIES Best Environmetrics Paper Award for ``A model for Antarctic Surface mass balance and ice core site selection,''  (Amount: Travel award and \$750).
\item 2019 STATMOS Workshop - Young Researcher Travel Award, 2019  (Amount: \$1,500)

\item James B. Duke Fellowship Recipient, Duke University, 2015-2019 (Amount: \$20,000)
\item ENVR Workshop - Statistics for the Environment: Research, Practice and Policy, Student travel award, 2018 (Amount: \$1,500)
\item Department of Statistical Science TA of the Year, 2018 (Amount: \$1,500)
\item Statistical Science First Year Fellowship, Duke University, 2015-2016 
\item Conference on Data Analysis Student Travel Award, 2014 (Amount: \$1,000)
\item Brigham Young University Student Research Conference Session Winner, 2014 and 2015

%\item Office of Research and Creative Activities Grant, Brigham Young University, 2014 (Amount: \$1,500)
%\item Statistics Department scholarship (masters), 2014-2015  (Amount: \$1,500)
%\item Outstanding Performance within the Second Year of Graduate School, Department of Statistics, Brigham Young University, 2015
%\item C. Bryant Copley Scholarship, Brigham Young University Physics Department, 2013-2014
%\item Dean's List, Brigham Young University, College of Life Sciences Dean's List (2008, 2010-2011); College of Physical and Mathematical Sciences Dean’s List (2011-2014)
%\item Distinguished Math Performance, Brigham Young University Department of Mathematics, 2011 and 2012
%\item Brigham Young University full-tuition scholarship, 2007-2008; 2010-2013 
%\item Brian Watkins Scholarship, 2007: for excellent high school student athletes
\end{enumerate}

\head{Statistical Consulting Experience}

\begin{enumerate}[label=$\bullet$]

\item Department of Clinical Sciences, North Carolina State University, College of Veterinary Medicine; Raleigh, NC; 2019 -- Present

\item Arbinger Institute; Farmington, Utah; 2019 -- 2020


\item Hare Lab, Duke University, Department of Evolutionary Anthropology; Durham, NC; 2017 -- 2019

\end{enumerate}



\head{Service}
\begin{enumerate}[label=$\bullet$]

\item Student Mentoring

\begin{table}[H]
\centering
\begin{tabular}{lll}
  \hline
Year Graduated & Student & Role \\ 
  \hline
  ------ & Caleb Dayley & MS Committee Chair \\
    ------  & Benjamin Dahl & Research Co-Mentor  \\ 
  ------ & Jason Meziere & Ph.D. Committee Member (Physics) \\
    2022  & Carly Lundgreen & Research Co-Mentor  \\ 
2021  & Daniel Sheanshang & MS Committee Chair  \\ 
2021  & Lynsie Warr & MS Committee Member  \\ 
2021  & Madeline Morris & MS Committee Member  \\ 
2020  & Maryanne Allen & Research Mentor  \\ 
2020  & Derik Mehl & Research Mentor \\ 
2020  & Spencer Ebert & MS Committee Member  \\ 
2020  & Shelby Taylor & MS Committee Member  \\ 
%2020  & Hannah Peterson & U of U MS Committee Member & Not yet completed  \\ 
   \hline
\end{tabular}
\end{table}


\item Departmental Service
\begin{enumerate}[label=$\cdot$]
\item Recruiting and Retention Committee (2021 - Present)
\item Comprehensive Exam Committee (2020 - Present)
\item Seminar Co-Coordinator (2019 - 2021)

\end{enumerate}

\item To Profession


%\end{enumerate}

\begin{enumerate}[label=$\cdot$]
\item Keynote speaker for Brigham Young University Mu Sigma Rho induction, 2021.
\item Organized or co-organized sessions for statistical conferences -- JSM 2020, CMStatistics 2021, QPRC 2022, and CMStatistics 2022.
\item Peer Review for: \emph{Annals of Applied Statistics (1); Biometrics (1); Electronic Journal of Statistics (2); Environmetrics (3); Journal of Agricultural, Biological and Environmental Statistics (1); Mathematical Inequalities \& Applications (1); Spatial and Spatio-temporal Epidemiology (1); Spatial Statistics (3); Statistics and Computing (1); Stochastic Environmental Research and Risk Assessment (1) }


\end{enumerate}
\end{enumerate}

\head{Memberships}

\begin{enumerate}[label=$\bullet$]
\item American Statistical Association: 2014-Present
\item International Society for Bayesian Analysis: 2017-Present
\item The International Environmetrics Society (TIES): 2021-Present
%\begin{enumerate}[label=$\cdot$]
%\item Section on Bayesian Statistical Science
%\item Section on Statistics and the Environment
%\item Section on Physical and Engineering Sciences
%\end{enumerate}
\end{enumerate}



%\head{Skills and Training}
%\begin{enumerate}[label=$\bullet$]
%\item Statistics
%\begin{enumerate}[label=$\cdot$]
%\item linear models, modern regression, Bayesian methods, multivariate methods, probability/measure theory, mixed models, generalized linear models, survival analysis, computational statistics, mathematical statistics
%\end{enumerate}
%\item Physics
%\begin{enumerate}[label=$\cdot$]
%\item mathematical physics, mechanics, quantum mechanics, electromagnetism, wave physics, acoustics, computational physics, and experimental methods
%\end{enumerate}
%\item Computation
%\begin{enumerate}[label=$\cdot$, rightmargin=1.5cm]
%\item R, MATLAB, C, C++, Python, Julia, SAS, Mathematica, Labview
%\item Linux, Git, Bash
%\end{enumerate}
%\end{enumerate}


\end{document}
